### 2025-09-24 paper/sec/evaluation.tex

\subsection{Success Rate by Category}
To evaluate the system we used a sample of the \SciGen dataset~\citep{scigen_dataset_2021}.

We aggregated the generated expression in three categories: aggregation, trends, quantitative (See
Table~\ref{tab:natural-language-forms}). \figref{success_rate_by_category} shows the results obtained in
generating expression by categories.

@@

>>>>

\subsection{Success Rate by Category}
To evaluate the system we used a sample of the \SciGen dataset~\citep{moosavi21}. We aggregated the generated
expression in three categories: aggregation, trends, quantitative (See
Table~\ref{tab:natural-language-forms}). \figref{success_rate_by_category} shows the results obtained in
generating expression by categories.

@@

\subsection{Counterfactual testing}
\label{subsec:validation-with-counterfactual-data}

For the \emph{counterfactual testing} part of our analysis, the input data is deliberately modified in order
to verify the consistency of the behaviours. Both the expected and generated expressions are executed again
and the results are compared. If discrepancies are found \rpnote{complete}
